\documentclass{article}[11pt]
\input{preamble}
%\usepackage{times}

\def\diam{\mathrm{diam}}
\def\dist{\mathrm{dist}}
\def\mckc{{\sffamily Heterogeneous Cap-$k$-Center}\xspace}
%\def\cckp{{\sffamily Cardinality-Constrained Knapsack Cover}\xspace}
\def\cckp{$Q|f_i|C_{min}$\xspace}
\def\opt{\mathsf{OPT}}
\def\capkc{{\sffamily Cap-$k$-Center }}
\def\x{{\mathsf x}}
\def\y{y^{{\mathsf{int}}}}
\def\z{\bar{z}}
\def\Supp{\mathsf{Supp}\xspace}
\def\n{n^{(1)}}
\def\nn{n^{(2)}}
\def\effc{c_{\mathrm{eff}}}
\def\zz{z^{\mathsf{int}}}
\def\suff{\mathsf{suff}}
\def\Sone{\calS_{\mathsf{round}}}
\def\Stwo{\calS_{\mathsf{nexp}}}

\def\Cb{C_{\mathsf{blue}}}
\def\Cbb{C_{\mathsf{black}}}
\def\Cr{C_{\mathsf{red}}}
\def\Cp{C_{\mathsf{purple}}}
\def\Cd{C_{\mathsf{del}}}

%\newcommand{\gset}{Y}
%\newcommand{\gcol}{{\cal Y}}
\newcommand{\brp}{{(p)}}
\renewcommand{\br}[1]{{(#1)}}
\newcommand{\bc}{{\bar c}}
\renewcommand{\epsilon}{\varepsilon}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}


\usepackage[colorinlistoftodos,textsize=tiny,textwidth=2cm,color=red!25!white,obeyFinal]{todonotes}
\newcommand{\aknote}[1]{\todo[color=green!25!white]{AK: #1}\xspace}
\newcommand{\rknote}[1]{\todo[color=red!25!white]{RK: #1}\xspace}
\newcommand{\dcnote}[1]{\todo[color=yellow!25!white]{DC: #1}\xspace}



\begin{document}
\title{\huge The Heterogeneous Capacitated $k$-Center Problem}
\date{}
\author{Deeparnab Chakrabarty \\ \small Microsoft Research India\\\small  deeparnab@gmail.com \and Ravishankar Krishnaswamy \\ \small Microsoft Research India\\\small  ravishankar.k@gmail.com \and Amit Kumar \\ \small  Comp. Sci. \& Engg., IIT Delhi \\ \small amitk@cse.iitd.ac.in}
\maketitle
\begin{abstract}
	The abstract goes here.
\end{abstract}
\thispagestyle{empty}
\newpage
\setcounter{page}{1}
\input{section1}
\input{preliminaries}
\input{section2}
\input{section3}
\input{section5}
\input{section4}
\input{section6}
\input{section7}
\input{section8}
%\section{Conclusion}
\bibliographystyle{alpha}
\bibliography{mckc}
\newpage
\appendix


\section{Integrality Gap for Non-Uniform Santa Claus Problem}
We reproduce the integrality gap example for the configuration LP by Bansal and Sviridenko~\cite{BS} for the general max-min allocation problem, and point out how their instance is in fact a $Q|restr|C_{min}$ instance.
Fix integer $K$. There are $K$ machines with demand $D_i = K$; these are the large machines $L = \{M_1,M_2,\ldots,M_K\}$. There are $K-1$ large jobs with $c_j = K$ which can only be assigned to the machines in $L$.
Let $J_B$ be the set of large jobs. There are $K^2$ small machines each with $D_i = 1$; these machines are distributed in $K$ classes where the $i$th class $\cC_i$ contains $K$ small machines. We let $m^{(i)}_k$ denote the $k$th machine in $\cC_i$, for $1\leq k\leq K$.
There are $K^2 + K$ small jobs with $c_j = 1$. These jobs are partitoned into $K$ classes with $i$th class $\cJ_i$ containing $K+1$ small jobs. Each class $\cJ_i$ has one ``public'' job $j^{(i)}_0$ which can be assigned to any machine $m^{(i)}_k \in \cC_i$
 and $K$ ``private'' jobs $j^{(i)}_k$, $1\leq k\leq K$ where $j^{(i)}_k$ can be assigned to only $m^{(i)}_k \in \cC_i$. Furthermore all the private jobs $j^{(i)}_k\in \cJ_i$ can be assigned to the large machine $M_i \in L$. This completes the description of the instance.
Note that the number of machines and jobs are $\Theta(K^2)$.

The integral optimum solution must give one machine $i$ capacity $\leq D_i/K$. Indeed, at least one large machine $M_i$ will not receive a job in $J_B$.
The only other jobs available to $M_i$ are the private jobs in $\calJ_i$. Suppose we allocate two such jobs to $M_i$; wlog these are $j^{(i)}_1$ and $j^{(i)}_2$. Now note
that the machines $m^{(i)}_1$ and $m^{(i)}_2$ have only job $j^{(i)}_0$ which can be assigned to them; and so one of them would get capacity $0$.
Therefore, the machine $M_i$ can receive only one job $j^{(i)}_k$ giving it total capacity $\leq D_i/K$.

On the other hand the configuration LP is feasible. Every large machine $M_i$ gets $z(M_i, j) = 1/K$ for all large jobs $j\in J_B$ and $z(M_i,\{j^{(i)}_1,\ldots, j^{(i)}_K\}) = 1/K$ for the set of private jobs in $\cJ_i$.
For all $1\leq i,k\leq K$, every machine $m^{(i)}_k$ receives $z(m^{(i)}_k,j^{(i)}_k) = 1-1/K$ and $z(m^{(i)}_k,j^{(i)}_0) = 1/K$. One can check all the jobs are fractionally assigned exactly.


\newpage%\newpage
\listoftodos


\end{document}
